% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass [margin] {res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Arun Rathakrishnan\\[12.5pt]} % the \\[12pt] adds a blank line after name
 
\address{ 
rathakrishnanarun@gmail.com \\
https://github.com/r-arun  \\
        (631) 944-0302 
}
\address{Department of Computer Science \\ Stony Brook University \\ NY 11790 \\
         }

 
\begin{resume} 
 
\section{Education} 
M.S in Computer Science \hfill Aug 2012 - Present \\
Stony Brook University\\
GPA: 3.5/4.0 

B.E in Computer Science \& Engineering \hfill Jul 2006 - May 2010\\
Anna University, Madras Institute of Technology \\
GPA: 8.46/10.0
\section{Experience}
 Applications Developer, iNautix Technologies Limited \hfill Jun 2010 - Jul 2012
% \begin{itemize} \itemsep -2pt  % reduce space between items
% \item Worked on the NetX 360 Product suite
% \item Authored a Web based tool for retrieving logs and generating reports.
% \item Authored a suite of scripts for monitoring the operational activity.
% \end{itemize}
 
\section{Projects} 
		Parallel Breadth First Search \hfill   Mar 2013
                \begin{itemize} \itemsep -2pt
                 \item An optimal parallel algorithm for Breadth First Search in Cilk model.
                 \item An implementation of the algorithm in Cilk++.
		 \end{itemize}

		Parallel Connected Components Algorithms \hfill   Apr 2013
                \begin{itemize} \itemsep -2pt
				\item Github: https://github.com/fizzfaldt/cse638-hw/tree/master/hw2
                 \item Parallel implementation of several algorithms for finding\\
				 connected components in a graph, in Cilk++.
		 \end{itemize}

		Waiter Problem \hfill   May 2013
                \begin{itemize} \itemsep -2pt
		\item Github: https://github.com/r-arun/cse523
                 \item Heuristics for balancing weights on a surface.
		 \end{itemize}

		Stackable Encrypted File System \hfill   May 2013
                \begin{itemize} \itemsep -2pt
                 \item wrapfs based encrypted file system.
                 \item Encryption/Decryption is performed on file data in page buffers.
		 \end{itemize}

	   Decision Tree Classifier    \hfill         Nov 2012 
                \begin{itemize} \itemsep -2pt
		\item Github: https://github.com/r-arun/AI-project
              \item For classification of data based on approval of loan to applicants.
		 \end{itemize}

		Vocabulary Builder \hfill   May 2011
                \begin{itemize} \itemsep -2pt
		\item Github: https://github.com/r-arun/word
                 \item An application for improving and testing your vocabulary for GRE.
		 \end{itemize}

               An Implementation of grep    \hfill         Apr 2008 
                \begin{itemize} \itemsep -2pt
              \item Extends grep to support sub-expressions.            
                \item Support for both NFA and Minimized DFA representations.

		 \end{itemize}

	
%Tabulate Computer Skills; p{3 in}% defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{rl p{3in}}
   Advanced Level & C, Python \\
   Intermediate Level & Java, STL, vim \\
   Basic Level & JavaScript, C++, Perl, git, LaTeX, bash, sed, Eclipse \\
\end{tabular}


\section{Co-curricular Activities}
\begin{itemize} \itemsep -2pt
\item Member of teams that qualified for ACM ICPC Regionals in 2012 (Greater New York Region - 9th place) and 2008 (Asia - Kerala - 16th place).
\item Among the Top 5 teams in the onsite programming contest at Kurukshetra, a national level symposium at College of Engineering, Anna University.
\end{itemize}

\end{resume} 
\end{document} 



